---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.show = "hide",
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggwebthemes

<!-- badges: start -->
<!-- badges: end -->

This R package contains some themes for <font size="4">``ggplot2``</font> that were optimized for use in blogs and for similar online usage. Package source code is available [on GitLab](https://gitlab.com/peterbar/ggwebthemes). You can find a post about this package on [Data Enthusiast's Blog](https://dataenthusiast.ca/).

Note: the package repository is also mirrorred to GitHub, primarily in order for <font size="4">``available::available("ggwebthemes")``</font> to show that the package name was taken; <font size="4">``ggwebthemes``</font> home is on GitLab.

Submit bug reports, issues, and feature requests [here](https://gitlab.com/peterbar/ggwebthemes/-/issues).

## Installation

The package is not yet on CRAN. You can install <font size="4">``ggwebthemes``</font> from GitLab:

``` r
# option 1: install using devtools
devtools::install_gitlab("peterbar/ggwebthemes")
    
# option 2: install using remotes
remotes::install_gitlab("peterbar/ggwebthemes")
```

## Examples

```{r example}
library(ggwebthemes)
library(palmerpenguins)


# theme_web_bw()
ggplot(penguins, aes(x = bill_length_mm, y = body_mass_g)) +
  facet_wrap(~ species, scales = "free_x") +
  geom_point(size = 2, na.rm = TRUE) +
  geom_smooth(formula = y ~ x,
              method = "lm",
              se = FALSE,
              na.rm = TRUE) +
  theme_web_bw() +
  labs(x = "Bill length, mm",
       y = "Body mass, grams",
       title = "Body Mass vs. Bill Length in Penguins",
       subtitle = "Grouped by Species",
       caption = "Data: Gorman, Williams, and Fraser 2014")


# theme_web_classic()
ggplot(penguins, aes(x = bill_length_mm, y = body_mass_g)) +
  facet_wrap(~ species, scales = "free_x") +
  geom_point(size = 2, na.rm = TRUE) +
  geom_smooth(formula = y ~ x,
              method = "lm",
              se = FALSE,
              na.rm = TRUE) +
  theme_web_classic() +
  labs(x = "Bill length, mm",
       y = "Body mass, grams",
       title = "Body Mass vs. Bill Length in Penguins",
       subtitle = "Grouped by Species",
       caption = "Data: Gorman, Williams, and Fraser 2014")


# theme_web_void()
ggplot(penguins, aes(x = bill_length_mm, y = body_mass_g)) +
  facet_wrap(~ species, scales = "free_x") +
  geom_point(size = 2, na.rm = TRUE) +
  geom_smooth(formula = y ~ x,
              method = "lm",
              se = FALSE,
              na.rm = TRUE) +
  theme_web_void() +
  labs(x = "Bill length, mm",
       y = "Body mass, grams",
       title = "Body Mass vs. Bill Length in Penguins",
       subtitle = "Grouped by Species",
       caption = "Data: Gorman, Williams, and Fraser 2014")
```
